Dynein walks like an Imperial AT-ST

### 2017-11-07 reorganize/papers/paper/supplemental-figs.tex
Add new supplemental figure.

\begin{figure}%[tbhp]
\centering
 \begin{minipage}{0.5\textwidth}
   \centering
   \includegraphics[width=\linewidth]{figures/schematic-prestroke}
   \label{fig:prestrokeangle}
 \end{minipage}%
 \begin{minipage}{0.5\textwidth}
   \centering
   \includegraphics[width=\linewidth]{figures/schematic-poststroke}
   \label{fig:poststrokeangle}
 \end{minipage}
 %
 \begin{minipage}{\textwidth}
   \centering
   \includegraphics[width=\linewidth]{figures/schematic-binding-angle}
   \label{fig:bindingangle}
 \end{minipage}
\caption{\textbf{Schematic of model equilibrium angles over cryo-EM images.} \textbf{a.)} Prestroke and \textbf{b.)} poststroke dynein heavy chains superimposed with model motor angles, both from \cite{burgess-paper}. \textbf{c.)} Axonemal dynein bound to MT with model binding angle superimposed, from \cite{leschziner}.}
\label{fig:modelangles}
\end{figure}

>>>>

\begin{figure}%[tbhp]
\centering
 \begin{minipage}{0.5\textwidth}
   \centering
   \includegraphics[width=\linewidth]{figures/schematic-prestroke}
   \label{fig:prestrokeangle}
 \end{minipage}%
 \begin{minipage}{0.5\textwidth}
   \centering
   \includegraphics[width=\linewidth]{figures/schematic-poststroke}
   \label{fig:poststrokeangle}
 \end{minipage}
 %
 \begin{minipage}{\textwidth}
   \centering
   \includegraphics[width=\linewidth]{figures/schematic-binding-angle}
   \label{fig:bindingangle}
 \end{minipage}
 \begin{minipage}{\textwidth}
   \centering
   \includegraphics[width=\linewidth]{figures/schematic-full}
   \label{fig:allangles}
 \end{minipage}
\caption{\textbf{Schematic of model equilibrium angles over cryo-EM images.} \textbf{a.)} Prestroke and \textbf{b.)} poststroke dynein heavy chains superimposed with model motor angles, both from \cite{burgess-paper}. \textbf{c.)} Axonemal dynein bound to MT with model binding angle superimposed, from \cite{leschziner}. \textbf{d.} Full native dynein cryo-EM image bound to an MT with model superimposed, from \textbf{nativestructure}.}
\label{fig:modelangles}
\end{figure}
